%-------------------------
% Resume in Latex
% Author : Kerim Kochekov
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Kerim Kochekov}} & \textbf{Email:} \href{mailto:kerim.kocekow@gmail.com}{kerim.kocekow@gmail.com}\\
  \href{https://github.com/KerimKochekov} {\textbf{Github:} {www.github.com/kerimkochekov}} & \href{https://www.linkedin.com/in/kerimkochekov/}{\textbf{Linkedin:} {www.linkedin.com/in/kerimkochekov}} \\
  \textbf{Languages:} {Python, C/C++, Java, SQL, Javascript} & \textbf{Technologies:} {AWS, Git, Django, NodeJS} \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Hong Kong University of Science and Technology, PhD}{Sept 2022 -- Aug 2026 (expected)}
      {Research area: Parameterized algorithms (Theoretical Computer Science).}{}
      \begin{itemize}
          \item Passed the interview process with a success rate of 1.7\% (number of offers/number of interviewees).
          \item Won scholarship of Hong Kong PhD Fellowship Scheme (HKPFS) of HK\$1,445,200 (approximately US\$184,100) by selecting among the best and brightest 300 students over the world for 2022.
      \end{itemize}
    \resumeSubheading
      {Innopolis University, BSc in Computer Science (Data science)}{Aug 2018 -- Aug 2022}
      {Related Coursework: Computer Vision, Practical ML and DL, Big Data, Data mining}{}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
   \resumeSubheading
      {Morphy Capital}{Istanbul, Turkey}
      {Quantitative Researcher}{May 2022 - August 2022}
      \resumeItemListStart
         \resumeItem{Feature engineering}
        {Developed an analytical feature selection algorithm for designed models consisting of dynamic 20+ variables (specific to stock data).}
         \resumeItem{Machine learning model}
        {Constructed model for BIST-30 (most popular 30 stocks of Istanbul stock market with the largest market capitalization) using Catboost (gradient boosting tree algorithm) and outperformed predictions of baselines of the company by 9\% with the help of model and feature selection algorithm. }
         \resumeItem{Analysis}
        {Investigated the relationship between the BIST-30 stocks to generate correlation data for my developing machine learning algorithm and introduced new 6 metrics for evaluating the model performance.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Codechef, Unacademy}{Remote}
      {Problem Setter}{December 2021 - April 2022}
      \resumeItemListStart
        \resumeItem{Problem setting}
        {Set innovative algorithm problems for monthly challenges of Codechef for thousands of people.}
        \newline
        \textbf{Problems link}: \href{https://www.codechef.com/tags/problems/mrkerim}{www.codechef.com/tags/problems/mrkerim}
        \resumeItem{Project}
        {Worked on a "Curated learning" project for preparing hints and auxiliary editorials for beginner-level programmers to solve algorithmic tasks and puzzles.}
        \resumeItem{Tag labeling}
        {Determined algorithmic labels for a certain amount of hard tasks that can be helpful to participants in case they fail to solve problems.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Innopolis University, Lab of Software development}{Remote}
      {Data Engineer}{May 2021 - July 2021}
      \resumeItemListStart
        \resumeItem{SQL filtration}
          {Worked together with the Department of Education to retrieve data using Moodle API. Filtered the retrieved data using SQL to prepare the periodic local database for newly developing application.}
        \resumeItem{Django application}
          {Developed an application with my team for helping professors and administrators track the grading status of all assignments of all courses for some term. Implemented backend with Django and fed the application with my prepared local database. To conclude the project and present it to university administration, we deployed the application to simple MVP with basic frontend using Javascript.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Innopolis University, Lab of Autonomous Transport Systems}{Innopolis, Russia}
      {Intern Researcher (Data scientist)}{May 2019 - June 2019}
      \resumeItemListStart
        \resumeItem{Research}
          {Investigated effective augmentation techniques with the prepared autonomous vehicle datasets.}
        \resumeItem{Reports}
          {Wrote weekly statistical reports about the results and findings of each week’s research.}
        \resumeItem{Framework}
          {Developed an adaptive classical augmentation model in Tensorflow for an autonomous vehicle project.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


   
%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Distributed Online Judge}{\href{https://github.com/IU-MAP/project-distributed-online-judge}{www.github.com/IU-MAP/project-distributed-online-judge}}
      \begin{itemize}
      \item{Build a simple distributed computing application for testing programs/problems against test cases in programming competitions with my team. The project was an attempt to port the approach of Lichess’s computer analysis feature to competitive programming platforms to donate your machine(CPU, memory) for the system to disburden the server to test other participants' submissions in a fast way without tackling and need of the load-balancer. 
      \item{The backend of the project implemented by me in Django, and the frontend of the application implemented by my
teammates in React. Moreover, I helped of developing the script in Linux for testing the solution against provided
test cases for that problem.}}
      \end{itemize}
    \resumeSubItem{Distributed File System (DFS)}{\href{https://github.com/KerimKochekov/DFS}{www.github.com/KerimKochekov/DFS}}
      \begin{itemize}
      \item{Implemented the DFS with the master and slave strategy (in terms of namenode and datanodes) in the RPyC library of Python.}
      \item{Configured replication strategy (similar to the strategy of HDFS) to not lose files in case of some datanodes are down.}
      \item{Deployed a project to AWS with a help of Docker to test scalability and fault tolerance.}
      \end{itemize}
      
  \resumeSubHeadingListEnd
%-----------Hobbies----------------
\section{Leadership / Activities}
\resumeSubHeadingListStart
 \resumeSubheading
      {Inzva}{Remote}
      {Volunteer Lead and Problem Setter}{August 2021 - September 2022}
      \resumeItemListStart
        \resumeItem{Prepared and tested algorithmic problems}
          {As part of the organizing team (lead for 2022) set innovative algorithmic problems for the Online Programming Competition 2021 and 2022, which is also considered the biggest competitive programming competition in Turkey. Furthermore, I helped to test other problem setters’ challenging tasks to strengthen their prepared test cases. \href{https://inzva.com/reports/2021/online-programming-contest-for-universities-2021-report}{\textit{www.inzva.com/reports/2021/online-programming-contest-for-universities-2021-report}}}
      \resumeItemListEnd
      
      \resumeSubheading
          {Seoul National University}{Seoul, South Korea}
          {Exchange student}{March 2020 - June 2020}
          \resumeItemListStart
            \resumeItem{Study}
              {Took graduate (MSc) courses as a BSc student during the exchange program.}
            \resumeItem{Research}
              {Proposed new ideas for optimizing video upload for time-shifted viewing of social live streams.}
            \resumeItem{Project (Mini-Relational Database System)}
      {Build a simplified relational database system composed of 5 layers: buffer-pool layer, paged-file layer,
heap-file layer, access-method layer, and front-end layer. Project implemented in C language. 
\newline
\textbf{Project link:}
\href{https://github.com/KerimKochekov/Database-Systems}{www.github.com/KerimKochekov/Database-Systems}}
          \resumeItemListEnd
    \resumeSubheading
      {Hackerrank}{Remote}
      {Lead and Problem Setter}{October 2017 - December 2017}
      \resumeItemListStart
        \resumeItem{Created problems}
          {As a leader of the organizing team and problem setter of the contest created 5 novel problems for an International programming contest named ”101Hack 52” with over 3500 participants on the platform.
          \textbf{Contest link: }\href{https://hackerrank.com/101hack52}{{www.hackerrank.com/101hack52}}}
      \resumeItemListEnd
    \resumeSubHeadingListEnd

  



\section{Awards}
  \resumeSubHeadingListStart
    \resumeSubItem{Google Kick Start rounds}{}
      \begin{itemize}
      \item{\textbf{2022 Round D:} ranked 45th place over 8062 participants (top 0.5\%)}
      \item{\textbf{2022 Round B:} ranked 330th place over 5716 participants (top 5\%)}
      \item{\textbf{2021 Round B:} ranked 59th place over 7398 participants (top 1\%)}
      \item{\textbf{2021 Round A:} ranked 242th place over 19840 participants (top 1\%)}
      \item{\textbf{2020 Round G:} ranked 280th place over 8132 participants (top 3\%)}
      \item{\textbf{2020 Round C:} ranked 262th place over 13650 participants (top 2\%)}
      \end{itemize}
   \resumeSubItem{ACM ICPC Northern Euroasia 2018, 2020 and 2022}{3rd-degree diploma}
    \resumeSubItem{Meta Hackercup 2021 3rd round}{ranked 343th place over 34585 participants (top 1\%)}
    \resumeSubItem{Google Hash Code 2019}{ranked 101st place over 6647 teams (top 2\%)}
   \resumeSubItem{International Olympiad in Informatics 2018}{Bronze medal}
   \resumeSubItem{Asian-Pacific Olympiad in Informatics 2017}{Bronze medal}
   \resumeSubItem{International Zhautykov Olympiad in Informatics (Computer Science) 2018}{Silver medal}

  \resumeSubHeadingListEnd

\end{document}
